\thesistitle

### 2019-07-30 sections/research.tex
Fixed the examples
Better (minimal) T3R example

void doDEF(){
  doA();
  doB("def");
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doABC(){
	printNice("abc");
}

void doDEF(){
	printNice(s, "def");
}

@@

void doADC(){
  doA();
  doD();
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doABC(){
	printNice(this::doB);
}

void doDEF(){
	printNice(this::doD);
}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/type3_3}
  \caption{Added statement between cloned methods.}
  \label{fig:type3}
\end{figure}

In figure \ref{fig:type3} a single statement is added. This statement is found in between cloned lines. We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}. This gap has a threshold for type 3R, which is calculated by the following formula:

>>>>

void doDEF(){
  doA();
  doB("def");
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doABC(){
	doThis("abc");
}

void doDEF(){
	doThis(s, "def");
}

@@

void doADC(){
  doA();
  doD();
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doABC(){
	doThis(this::doB);
}

void doADC(){
	doThis(this::doD);
}

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
void doCwithA(){
	int a = getA();
	doC(a);
}

void multiplyA(){
  int a = getA();
  a *= 5;
  doC(a);
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doCwithA(){
	modifyA(false);
}

void multiplyA(){
	modifyA(true);
}

void modifyA(boolean multiply){
  int a = getA();
  if(multiply) a *= 5;
  doC(a);
}
\end{javacode}}
\end{parcolumns}
\caption{Added statement between cloned fragments refactored.}
\label{fig:type3}
\end{figure}

In figure \ref{fig:type3} a single statement is added. This statement is found in between cloned lines. There is a \textit{gap} of non-cloned lines in between two clone classes. For type 3R, the size of this gap is bounded by a threshold. It is calculated by the following formula:
